The human in the loop: volunteer computing as a socio-technical system

### 2016-03-09 PPSN2016/paper.Rnw
R is the most irritant thing ever

%\documentclass[letterpaper]{article}
%\usepackage{natbib,alifeconf}
%\usepackage[breaklinks=true]{hyperref}
%\usepackage{url}

@@

\begin{document}
\title{The human in the loop: volunteer computing as a socio-technical
system}

>>>>

@@

\begin{document}

<<setup, cache=FALSE,echo=FALSE>>=
library("ggplot2")
experiment.data <- <- data.frame(Experiment=character(),
                                 newgraph = character(),
                                 nooverlap = character(),
                                 reboot = character(),
                                 cachereboot = character(),
                                 milliseconds=character(),                           
                                 IPs=character(), 
                                 actualIPs=character(),
                                 PUTs=character(),
                                 actualPUTs=character())
these.experiments <- c("nooverlap-1","nooverlap-newgraph", "nooverlap-newgraph-2","nooverlap-newgraph-3","nooverlap-newgraph-reboot")

for ( i in these.experiments ) {
    print(i)
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-time-cache-2016-03-cache=32-",i,".csv"))
    newgraph = TRUE
    nooverlap = TRUE
    reboot = TRUE
    cachereboot = TRUE
    if ( ! grep("newgraph",i)) {
        newgraph = FALSE
    }
    if ( ! grep("noover",i)) {
        nooverlap = FALSE
    }
    if ( ! grep("reboot",i)) {
        reboot = FALSE
    }
    if ( ! grep("cache",i)) {
        cachereboot = FALSE
    }

    these.experiments <- rbind( these.experiments,
                               data.frame( Experiment=rep(i, length(this.data$IPs)),
                                          newgraph = rep(newgraph, length(this.data$IPs)),
                                          nooverlap = rep(nooverlap, length(this.data$IPs)),
                                          reboot = rep(reboot, length(this.data$IPs)),
                                          cachereboot = rep(cachereboot, length(this.data$IPs)),
                                          milliseconds=this.data$milliseconds,
                                          IPs=this.data$IPs,
                                          actualIPs=this.data$actualIPs,
                                          PUTs=this.data$PUTs,
                                          actualPUTs=this.data$actualPUTs))
}

@
\title{The human in the loop: volunteer computing as a socio-technical
system}
